---
title: "Raclo_FLB_4_paper"
author: "Tove Freiburghaus"
date: '2020-02-06'
output: html_document
---

Part 1. Freesurfer data. 

:::::::::::::::::::::::::::::::::::::::::::::::::


Import BPNDs. PET2 is raclopride data- evening runs (all subjects have gone thorugh this), PET4 is FLB data, all subjects have gone thorugh this.
```{r}
library(readxl)
PET2_SRTM <- read_excel("X:/kipet/atlas_images/human/vff/Tove/RLS/BPNDs/PET2_SRTM.xls")

library(readxl)
PET4_SRTM <- read_excel("X:/kipet/atlas_images/human/vff/Tove/RLS/BPNDs/PET4_SRTM.xls")


```

function for getting descriptve data:
```{r}
## Summarizes data.
## Gives count, mean, standard deviation, standard error of the mean, and confidence interval (default 95%).
##   data: a data frame.
##   measurevar: the name of a column that contains the variable to be summariezed
##   groupvars: a vector containing names of columns that contain grouping variables
##   na.rm: a boolean that indicates whether to ignore NA's
##   conf.interval: the percent range of the confidence interval (default is 95%)
summarySE <- function(data=NULL, measurevar, groupvars=NULL, na.rm=TRUE,
                      conf.interval=.95, .drop=TRUE) {
    library(plyr)

    # New version of length which can handle NA's: if na.rm==T, don't count them
    length2 <- function (x, na.rm=FALSE) {
        if (na.rm) sum(!is.na(x))
        else       length(x)
    }

    # This does the summary. For each group's data frame, return a vector with
    # N, mean, and sd
    datac <- ddply(data, groupvars, .drop=.drop,
      .fun = function(xx, col) {
        data.frame(ROI  = measurevar, 
          N  = length2(xx[[col]], na.rm=na.rm),
          mean = mean (xx[[col]], na.rm=na.rm),
          sd   = sd (xx[[col]], na.rm=na.rm)
        )
      },
      measurevar
    )


    

    datac$se <- datac$sd / sqrt(datac$N)  # Calculate standard error of the mean, add that column

    # confidence interval multiplier for standard error
    # Calculate t-statistic for confidence interval: 
    # e.g., if conf.interval is .95, use .975 (above/below), and use df=N-1
    ciMult <- qt(conf.interval/2 + .5, datac$N-1)
    datac$ci <- datac$se * ciMult #add column of confidence interval

    return(datac)
}
```


Get all descriptive stats in one data frame. 
```{r}
library(plyr)
Raclo <- PET2_SRTM
FLB <- PET4_SRTM
Raclosum <- NULL
Raclosum <- data.frame()

Raclosum <- rbind(Raclosum, summarySE(data = Raclo,measurevar = "FC"))
Raclosum <- rbind(Raclosum, summarySE(data = Raclo,measurevar = "OC"))
Raclosum <- rbind(Raclosum, summarySE(data = Raclo,measurevar = "TC"))
Raclosum <- rbind(Raclosum, summarySE(data = Raclo,measurevar = "AMG"))
Raclosum <- rbind(Raclosum, summarySE(data = Raclo,measurevar = "CAU"))
Raclosum <- rbind(Raclosum, summarySE(data = Raclo,measurevar = "CER"))
Raclosum <- rbind(Raclosum, summarySE(data = Raclo,measurevar = "HIP"))
Raclosum <- rbind(Raclosum, summarySE(data = Raclo,measurevar = "INS"))
Raclosum <- rbind(Raclosum, summarySE(data = Raclo,measurevar = "PUT"))
Raclosum <- rbind(Raclosum, summarySE(data = Raclo,measurevar = "THA"))

Raclosum <- Raclosum[,-c(1,3)] #exclude unnecessary data
    # Rename the "mean" column   
colnames(Raclosum)<-c("ROI","mean_raclo","sd_raclo","se_raclo","ci_raclo")


FLBsum <- NULL
FLBsum <- data.frame()

FLBsum <- rbind(FLBsum,summarySE(data = FLB, measurevar = "FC"))
FLBsum <- rbind(FLBsum,summarySE(data = FLB, measurevar = "OC"))
FLBsum <- rbind(FLBsum,summarySE(data = FLB, measurevar = "TC"))
FLBsum <- rbind(FLBsum,summarySE(data = FLB, measurevar = "AMG"))
FLBsum <- rbind(FLBsum,summarySE(data = FLB, measurevar = "CAU"))
FLBsum <- rbind(FLBsum,summarySE(data = FLB, measurevar = "CER"))
FLBsum <- rbind(FLBsum,summarySE(data = FLB, measurevar = "HIP"))
FLBsum <- rbind(FLBsum,summarySE(data = FLB, measurevar = "INS"))
FLBsum <- rbind(FLBsum,summarySE(data = FLB, measurevar = "PUT"))
FLBsum <- rbind(FLBsum,summarySE(data = FLB, measurevar = "THA"))

FLBsum <- FLBsum[,-c(1,3)]
colnames(FLBsum)<-c("ROI","mean_FLB","sd_FLB","se_FLB","ci_FLB") #renamed into the name of mean_x


Statistics <- cbind(Raclosum,FLBsum)
Statistics <- Statistics[-c(6,8),-6] #removing extra column. 
sort <- c(2,1,3,6,7,4,8,5)
Statisticssort <- cbind(Statistics,sort)
Statisticssort2 <- Statisticssort[order(sort),]
Statistics <- Statisticssort2[,-10]

Statisticsexs <- Statistics[-c(7,8),] #REMOVE striatal!!
```

Table - correlation between raclopride and flb- average INS + CER REMOVED, only extrastriatal

correlation och ci för figur 1. - Exclude?
```{r}


correlationRacloFLB <- cor(Statisticsexs$mean_raclo,Statisticsexs$mean_FLB)

ci_lower <- NULL
ci_lower <- numeric()
ci_lower <- c(ci_lower,cor.test(Statisticsexs$mean_raclo,Statisticsexs$mean_FLB)$conf.int[1])


ci_upper <- NULL
ci_upper <- numeric()
ci_upper <- c(ci_upper,cor.test(Statisticsexs$mean_raclo,Statisticsexs$mean_FLB)$conf.int[2])


confidence_flb <- data.frame(ci_lower,ci_upper)

sq_R <- correlationRacloFLB^2

table_corrRacFLB <- data.frame(correlationRacloFLB, sq_R, confidence_flb)

writexl::write_xlsx(table_corrRacFLB, "X:/kipet/atlas_images/human/vff/Tove/Analysis in R/results/Table_corr_Raclo_FLB.xlsx")


```

Create a table including Hall data and mean BPNDs along with statistics. 
Table 1
```{r}


library(readxl)
MOP <- read_excel("X:/kipet/atlas_images/human/vff/Tove/RLS/Descriptive data_hall.xls", sheet = "MOP") #read table with values from Hall article.
MOP <- MOP[-c(2,4),] #remove cer and ins

Stat_hall <- cbind(MOP,Statistics)
Stat_hallx <- Stat_hall[,-3] #extra columns + cerebellum and insula removed

writexl::write_xlsx(Stat_hallx, "X:/kipet/atlas_images/human/vff/Tove/Analysis in R/results/Stat_hall.xlsx") #Table 1
```
Colorplot of all individuals' BPNDs using raclo vs FLB, excluding striatal

Figure 1

```{r}
#setwd("X:/kipet/atlas_images/human/vff/Tove/Results_R_RLS")
setwd("X:/kipet/atlas_images/human/vff/Tove/Analysis in R/results")
library(tidyverse)
library(plyr)

ROI <- c("OC","OC","OC","OC","OC","OC","OC","OC","OC","OC","OC","OC","OC","OC","OC","OC","FC","FC","FC","FC","FC","FC","FC","FC","FC","FC","FC","FC","FC","FC","FC","FC","TC","TC","TC","TC","TC","TC","TC","TC","TC","TC","TC","TC","TC","TC","TC","TC","HIP","HIP","HIP","HIP","HIP","HIP","HIP","HIP","HIP","HIP","HIP","HIP","HIP","HIP","HIP","HIP","THA","THA","THA","THA","THA","THA","THA","THA","THA","THA","THA","THA","THA","THA","THA","THA","AMG","AMG","AMG","AMG","AMG","AMG","AMG","AMG","AMG","AMG","AMG","AMG","AMG","AMG","AMG","AMG")


RacloAll <- c(PET2_SRTM$OC,PET2_SRTM$FC,PET2_SRTM$TC,PET2_SRTM$HIP,PET2_SRTM$THA,PET2_SRTM$AMG)

FLBAll <- c(PET4_SRTM$OC,PET4_SRTM$FC,PET4_SRTM$TC,PET4_SRTM$HIP,PET4_SRTM$THA,PET4_SRTM$AMG)

allBP <- data.frame(ROI,RacloAll,FLBAll)


neworder <- c("OC","FC","TC","HIP","THA","AMG")
allBP2 <- arrange(transform(allBP,
             ROI=factor(ROI,levels=neworder)),ROI)
col <- ggplot(allBP2,aes(x=FLBAll,y= RacloAll,color=ROI))+
  geom_point() + 
  geom_smooth(method = 'lm',se = F) +  
  facet_wrap(ROI ~ ., scales = 'free') +
  labs(y= "[11C]Raclopride",x = "[11C]FLB-457")+
  ggtitle("Correlation between [11C]Raclopride and [11C]FLB-457 BPND")+
  theme(plot.title = element_text(hjust =0.5)) + 
  theme_bw() 

print(col)
ggsave("AllBP_colorES.png") #Figure 1
```







Make a table with all BPNBs for raclo and flb, pet2 and 4 each roi in separate columns - Column 1 of table 2. 
```{r}



all_racloflb <- NULL
all_racloflb <- data.frame()
raclo_bp <- PET2_SRTM[,-c(7,9)] #remove data for insula and cer!
colnames(raclo_bp)<-c("Subject","OC_raclo","FC_raclo","TC_raclo","HIP_raclo","THA_raclo","AMG_raclo","CAU_raclo","PUT_raclo")


flb_bp <- PET4_SRTM[,-c(7,9)] #remove data for insula and cer!
colnames(flb_bp)<-c("Subject","OC_flb","FC_flb","TC_flb","HIP_flb","THA_flb","AMG_flb","CAU_flb","PUT_flb")


all_racloflb <- merge(x = raclo_bp,flb_bp,by = 'Subject') #Get the mean of BPNDs for raclopride and FLB for subject who have done morning and afternoon runs. ST?MMER!
correlation_all_racloflb <- NULL

correlation_all_racloflb <- c(correlation_all_racloflb, cor(all_racloflb$OC_raclo,all_racloflb$OC_flb))
correlation_all_racloflb <- c(correlation_all_racloflb, cor(all_racloflb$FC_raclo,all_racloflb$FC_flb))
correlation_all_racloflb <- c(correlation_all_racloflb, cor(all_racloflb$TC_raclo,all_racloflb$TC_flb))
correlation_all_racloflb <- c(correlation_all_racloflb, cor(all_racloflb$HIP_raclo,all_racloflb$HIP_flb))
correlation_all_racloflb <- c(correlation_all_racloflb, cor(all_racloflb$THA_raclo,all_racloflb$THA_flb))
correlation_all_racloflb <- c(correlation_all_racloflb, cor(all_racloflb$AMG_raclo,all_racloflb$AMG_flb))
correlation_all_racloflb <- c(correlation_all_racloflb, cor(all_racloflb$CAU_raclo,all_racloflb$CAU_flb))
correlation_all_racloflb <- c(correlation_all_racloflb, cor(all_racloflb$PUT_raclo,all_racloflb$PUT_flb))


ci_lower <- NULL
ci_lower <- c(ci_lower,cor.test(all_racloflb$OC_raclo,all_racloflb$OC_flb)$conf.int[1])
ci_lower <- c(ci_lower,cor.test(all_racloflb$FC_raclo,all_racloflb$FC_flb)$conf.int[1])
ci_lower <- c(ci_lower,cor.test(all_racloflb$TC_raclo,all_racloflb$TC_flb)$conf.int[1])
ci_lower <- c(ci_lower,cor.test(all_racloflb$HIP_raclo,all_racloflb$HIP_flb)$conf.int[1])
ci_lower <- c(ci_lower,cor.test(all_racloflb$THA_raclo,all_racloflb$THA_flb)$conf.int[1])
ci_lower <- c(ci_lower,cor.test(all_racloflb$AMG_raclo,all_racloflb$AMG_flb)$conf.int[1])
ci_lower <- c(ci_lower,cor.test(all_racloflb$CAU_raclo,all_racloflb$CAU_flb)$conf.int[1])
ci_lower <- c(ci_lower,cor.test(all_racloflb$PUT_raclo,all_racloflb$PUT_flb)$conf.int[1])



ci_upper <- NULL
ci_upper <- numeric()
ci_upper <- c(ci_upper,cor.test(all_racloflb$OC_raclo,all_racloflb$OC_flb)$conf.int[2])
ci_upper <- c(ci_upper,cor.test(all_racloflb$FC_raclo,all_racloflb$FC_flb)$conf.int[2])
ci_upper <- c(ci_upper,cor.test(all_racloflb$TC_raclo,all_racloflb$TC_flb)$conf.int[2])
ci_upper <- c(ci_upper,cor.test(all_racloflb$HIP_raclo,all_racloflb$HIP_flb)$conf.int[2])
ci_upper <- c(ci_upper,cor.test(all_racloflb$THA_raclo,all_racloflb$THA_flb)$conf.int[2])
ci_upper <- c(ci_upper,cor.test(all_racloflb$AMG_raclo,all_racloflb$AMG_flb)$conf.int[2])
ci_upper <- c(ci_upper,cor.test(all_racloflb$CAU_raclo,all_racloflb$CAU_flb)$conf.int[2])
ci_upper <- c(ci_upper,cor.test(all_racloflb$PUT_raclo,all_racloflb$PUT_flb)$conf.int[2])

sq_R <- correlation_all_racloflb^2

ROI <- c("OC","FC","TC","HIP","THA","AMG","CAU","PUT")
table_correlation_all_racloflb <- data.frame(ROI,correlation_all_racloflb, sq_R, ci_lower,ci_upper)
colnames(table_correlation_all_racloflb)[2] <- "correlation Raclopride to FLB" #change the column name

writexl::write_xlsx(table_correlation_all_racloflb, "X:/kipet/atlas_images/human/vff/Tove/Analysis in R/results/table_correlation_all_racloflb.xlsx")
```

:::::::::::::::::::::::::::::::::::::::::
Test - retest
:::::::::::::::::::::::::::::::::::::::::

Test- retest. 
Now I want to use the data that has not previously been used, data from PET1 and PET3. PET1 is the morning run of raclopride and PET3 is the morning run of FLB. Not all subjects have done each morning run.
```{r}
library(readxl)
PET1_SRTM <- read_excel("X:/kipet/atlas_images/human/vff/Tove/RLS/BPNDs/PET1_SRTM.xls")


library(readxl)
PET3_SRTM <- read_excel("X:/kipet/atlas_images/human/vff/Tove/RLS/BPNDs/PET3_SRTM.xls")

```


Test-retest: Column 2 and 3 of table 2
```{r}

all_raclo <- NULL
all_raclo <- data.frame()
raclo_morning <- PET1_SRTM[,-c(7,9)] #remove data for insula and cer!
colnames(raclo_morning)<-c("Subject","FC_morning","OC_morning","TC_morning","AMG_morning","CAU_morning","HIP_morning","PUT_morning","THA_morning")

raclo_afternoon <-PET2_SRTM[,-c(7,9)]
colnames(raclo_afternoon)<- c("Subject","FC_afternoon","OC_afternoon","TC_afternoon","AMG_afternoon","CAU_afternoon","HIP_afternoon","PUT_afternoon","THA_afternoon")

all_raclo <- merge(x = raclo_morning,raclo_afternoon,by = 'Subject')

ROI <- c("OC","FC","TC","HIP","THA","AMG","CAU","PUT")

#Correlate the BPNDs in the morning and afternoon
corrRaclo <- NULL
corrRaclo <- numeric()


corrRaclo <- c(corrRaclo,cor(all_raclo$OC_morning,all_raclo$OC_afternoon))
corrRaclo <- c(corrRaclo,cor(all_raclo$FC_morning,all_raclo$FC_afternoon))
corrRaclo <- c(corrRaclo, cor(all_raclo$TC_morning,all_raclo$TC_afternoon))
corrRaclo <- c(corrRaclo, cor(all_raclo$HIP_morning,all_raclo$HIP_afternoon))
corrRaclo <- c(corrRaclo, cor(all_raclo$THA_morning,all_raclo$THA_afternoon))
corrRaclo <- c(corrRaclo, cor(all_raclo$AMG_morning,all_raclo$AMG_afternoon))
corrRaclo <- c(corrRaclo,cor(all_raclo$CAU_morning,all_raclo$CAU_afternoon))
corrRaclo <- c(corrRaclo,cor(all_raclo$PUT_morning,all_raclo$PUT_afternoon))


ci_lower <- NULL
ci_lower <- numeric()
ci_lower <- c(ci_lower,cor.test(all_raclo$OC_morning,all_raclo$OC_afternoon)$conf.int[1])
ci_lower <- c(ci_lower,cor.test(all_raclo$FC_morning,all_raclo$FC_afternoon)$conf.int[1])
ci_lower <- c(ci_lower,cor.test(all_raclo$TC_morning,all_raclo$TC_afternoon)$conf.int[1])
ci_lower <- c(ci_lower,cor.test(all_raclo$HIP_morning,all_raclo$HIP_afternoon)$conf.int[1])
ci_lower <- c(ci_lower,cor.test(all_raclo$THA_morning,all_raclo$THA_afternoon)$conf.int[1])
ci_lower <- c(ci_lower,cor.test(all_raclo$AMG_morning,all_raclo$AMG_afternoon)$conf.int[1])
ci_lower <- c(ci_lower,cor.test(all_raclo$CAU_morning,all_raclo$CAU_afternoon)$conf.int[1])
ci_lower <- c(ci_lower,cor.test(all_raclo$PUT_morning,all_raclo$PUT_afternoon)$conf.int[1])

ci_upper <- NULL
ci_upper <- numeric()
ci_upper <- c(ci_upper,cor.test(all_raclo$OC_morning,all_raclo$OC_afternoon)$conf.int[2])
ci_upper <- c(ci_upper,cor.test(all_raclo$FC_morning,all_raclo$FC_afternoon)$conf.int[2])
ci_upper <- c(ci_upper,cor.test(all_raclo$TC_morning,all_raclo$TC_afternoon)$conf.int[2])
ci_upper <- c(ci_upper,cor.test(all_raclo$HIP_morning,all_raclo$HIP_afternoon)$conf.int[2])
ci_upper <- c(ci_upper,cor.test(all_raclo$THA_morning,all_raclo$THA_afternoon)$conf.int[2])
ci_upper <- c(ci_upper,cor.test(all_raclo$AMG_morning,all_raclo$AMG_afternoon)$conf.int[2])
ci_upper <- c(ci_upper,cor.test(all_raclo$CAU_morning,all_raclo$CAU_afternoon)$conf.int[2])
ci_upper <- c(ci_upper,cor.test(all_raclo$PUT_morning,all_raclo$PUT_afternoon)$conf.int[2])


sq_R <- corrRaclo^2

corrRacCi <- data.frame(ROI, corrRaclo, sq_R, ci_lower,ci_upper)


#####

all_FLB <-NULL
all_FLB <- data.frame()
FLB_morning <- PET3_SRTM[,-c(7,9)]
colnames(FLB_morning)<-c("Subject","FC_morning","OC_morning","TC_morning","AMG_morning","CAU_morning","HIP_morning","PUT_morning","THA_morning")

FLB_afternoon <- PET4_SRTM[,-c(7,9)]
colnames(FLB_afternoon)<- c("Subject","FC_afternoon","OC_afternoon","TC_afternoon","AMG_afternoon","CAU_afternoon","HIP_afternoon","PUT_afternoon","THA_afternoon")

all_FLB <- merge(x = FLB_morning,FLB_afternoon,by = 'Subject')

corrFLB <- NULL
corrFLB <- numeric()

corrFLB <- c(corrFLB,cor(all_FLB$OC_morning,all_FLB$OC_afternoon))
corrFLB <- c(corrFLB,cor(all_FLB$FC_morning,all_FLB$FC_afternoon))
corrFLB <- c(corrFLB,cor(all_FLB$TC_morning,all_FLB$TC_afternoon))
corrFLB <- c(corrFLB, cor(all_FLB$HIP_morning,all_FLB$HIP_afternoon))
corrFLB <- c(corrFLB,cor(all_FLB$THA_morning,all_FLB$THA_afternoon))
corrFLB <- c(corrFLB,cor(all_FLB$AMG_morning,all_FLB$AMG_afternoon))
corrFLB <- c(corrFLB, cor(all_FLB$CAU_morning,all_FLB$CAU_afternoon))
corrFLB <- c(corrFLB,cor(all_FLB$PUT_morning,all_FLB$PUT_afternoon))

ci_lower <- NULL
ci_lower <- numeric()
ci_lower <- c(ci_lower,cor.test(all_FLB$OC_morning,all_FLB$OC_afternoon)$conf.int[1])
ci_lower <- c(ci_lower,cor.test(all_FLB$FC_morning,all_FLB$FC_afternoon)$conf.int[1])
ci_lower <- c(ci_lower,cor.test(all_FLB$TC_morning,all_FLB$TC_afternoon)$conf.int[1])
ci_lower <- c(ci_lower,cor.test(all_FLB$HIP_morning,all_FLB$HIP_afternoon)$conf.int[1])
ci_lower <- c(ci_lower,cor.test(all_FLB$THA_morning,all_FLB$THA_afternoon)$conf.int[1])
ci_lower <- c(ci_lower,cor.test(all_FLB$AMG_morning,all_FLB$AMG_afternoon)$conf.int[1])
ci_lower <- c(ci_lower,cor.test(all_FLB$CAU_morning,all_FLB$CAU_afternoon)$conf.int[1])
ci_lower <- c(ci_lower,cor.test(all_FLB$PUT_morning,all_FLB$PUT_afternoon)$conf.int[1])

ci_upper <- NULL
ci_upper <- numeric()
ci_upper <- c(ci_upper,cor.test(all_FLB$OC_morning,all_FLB$OC_afternoon)$conf.int[2])
ci_upper <- c(ci_upper,cor.test(all_FLB$FC_morning,all_FLB$FC_afternoon)$conf.int[2])
ci_upper <- c(ci_upper,cor.test(all_FLB$TC_morning,all_FLB$TC_afternoon)$conf.int[2])
ci_upper <- c(ci_upper,cor.test(all_FLB$HIP_morning,all_FLB$HIP_afternoon)$conf.int[2])
ci_upper <- c(ci_upper,cor.test(all_FLB$THA_morning,all_FLB$THA_afternoon)$conf.int[2])
ci_upper <- c(ci_upper,cor.test(all_FLB$AMG_morning,all_FLB$AMG_afternoon)$conf.int[2])
ci_upper <- c(ci_upper,cor.test(all_FLB$CAU_morning,all_FLB$CAU_afternoon)$conf.int[2])
ci_upper <- c(ci_upper,cor.test(all_FLB$PUT_morning,all_FLB$PUT_afternoon)$conf.int[2])


sq_R <- corrFLB^2

ROI <- c("OC","FC","TC","HIP","THA","AMG","CAU","PUT")

corrFLBCi <- data.frame(ROI, corrFLB, sq_R, ci_lower,ci_upper)

#writexl::write_xlsx(stats_raclo, "X:/kipet/atlas_images/human/vff/Tove/Analysis in R/results/stats_raclo2.xlsx") #NOT NEEDED
#writexl::write_xlsx(stats_FLB, "X:/kipet/atlas_images/human/vff/Tove/Analysis in R/results/stats_FLB2.xlsx") #NOT NEEDED

#correlation between morning an afternoon
writexl::write_xlsx(corrRacCi, "X:/kipet/atlas_images/human/vff/Tove/Analysis in R/results/Tbl_corr_Raclo.xlsx") #column 3, table 2.
writexl::write_xlsx(corrFLBCi, "X:/kipet/atlas_images/human/vff/Tove/Analysis in R/results/Tbl_corr_FLB.xlsx")
#Column 2, table 2

```


::::::::::::::::::::::::::::::::::::::::::::::::::
GG-plot with morning runs correlated to afternoon runs - flb
:::::::::::::::::::::::::::::::::::::::::::::::::

Figure 2
```{r}

#Correlation in the form of a facet wrap:
setwd("X:/kipet/atlas_images/human/vff/Tove/Analysis in R/results")
library(tidyverse)

ROI <- c("FC","FC","FC","FC","FC","FC","FC","FC","OC","OC","OC","OC","OC","OC","OC","OC","TC","TC","TC","TC","TC","TC","TC","TC","AMG","AMG","AMG","AMG","AMG","AMG","AMG","AMG","HIP","HIP","HIP","HIP","HIP","HIP","HIP","HIP","THA","THA","THA","THA","THA","THA","THA","THA")

all_FLB <- merge(x = FLB_morning,FLB_afternoon,by = 'Subject')

morning <- c(all_FLB$FC_morning,all_FLB$OC_morning,all_FLB$TC_morning,all_FLB$AMG_morning,all_FLB$HIP_morning,all_FLB$THA_morning)

afternoon <- c(all_FLB$FC_afternoon,all_FLB$OC_afternoon,all_FLB$TC_afternoon,all_FLB$AMG_afternoon,all_FLB$HIP_afternoon,all_FLB$THA_afternoon)

FLB_plot <- data.frame(ROI,morning,afternoon)

neworder <- c("OC","FC","TC","HIP","THA","AMG")
FLB_plot2 <- arrange(transform(FLB_plot,
             ROI=factor(ROI,levels=neworder)),ROI)

flb <- ggplot(FLB_plot2,aes(x=morning,y= afternoon,color=ROI))+
  geom_point() + 
  geom_smooth(method = 'lm',se = F) +  
  facet_wrap(ROI ~ ., scales = 'free') +
  labs(y= "PET 1",x = "PET 2")+
  ggtitle("Correlation between [11C]FLB-457 PET 1 and PET 2")+
  theme(plot.title = element_text(hjust =0.5)) + 
  theme_bw() 

print(flb)
ggsave("corr_FLB_ampm_all.png") #Upper image of Figure 2.
```


::::::::::::::::::::::::::::::::::::::::::::::::::
GG-plot with morning runs correlated to afternoon runs - raclopride
:::::::::::::::::::::::::::::::::::::::::::::::::

Figure 2
```{r}

#Correlation in the form of a facet wrap:
setwd("X:/kipet/atlas_images/human/vff/Tove/Analysis in R/results")  
library(tidyverse)

ROI <- c("FC","FC","FC","FC","FC","FC","FC","FC","OC","OC","OC","OC","OC","OC","OC","OC","TC","TC","TC","TC","TC","TC","TC","TC","AMG","AMG","AMG","AMG","AMG","AMG","AMG","AMG","HIP","HIP","HIP","HIP","HIP","HIP","HIP","HIP","THA","THA","THA","THA","THA","THA","THA","THA")


all_raclo <- merge(x = raclo_morning,raclo_afternoon,by = 'Subject')


morning_r <- c(all_raclo$FC_morning,all_raclo$OC_morning,all_raclo$TC_morning,all_raclo$AMG_morning,all_raclo$HIP_morning,all_raclo$THA_morning)

afternoon_r <- c(all_raclo$FC_afternoon,all_raclo$OC_afternoon,all_raclo$TC_afternoon,all_raclo$AMG_afternoon,all_raclo$HIP_afternoon,all_raclo$THA_afternoon)

subjects <- c(all_raclo$Subject,all_raclo$Subject,all_raclo$Subject,all_raclo$Subject,all_raclo$Subject,all_raclo$Subject)

raclo_plot <- data.frame(ROI,morning_r,afternoon_r,subjects)

neworder <- c("OC","FC","TC","HIP","THA","AMG")
raclo_plot2 <- arrange(transform(raclo_plot,
             ROI=factor(ROI,levels=neworder)),ROI)

raclo <- ggplot(raclo_plot2,aes(x=morning_r,y= afternoon_r,color=ROI))+
  geom_point() + 
  geom_smooth(method = 'lm',se = F) +  
  facet_wrap(ROI ~ ., scales = 'free') +
  labs(y= "PET 1",x = "PET 2")+
  ggtitle("Correlation between [11C]raclopride PET 1 and PET 2")+
  theme(plot.title = element_text(hjust =0.5)) + 
  theme_bw() 

print(raclo)
ggsave("corr_raclo_ampm_all.png") #Lower image of Figure 2.


```

::::::::::::::::::::::::::::::::::::


SUPPLEMENTARY

::::::::::::::::::::::::::::::::::::

Correlation plot - including error bars
Supp Figure 1
```{r}
#setwd("X:/kipet/atlas_images/human/vff/Tove/Results_R_RLS")
setwd("X:/kipet/atlas_images/human/vff/Tove/Analysis in R/results")


rownames(Statisticsexs)<- Statisticsexs$ROI
library(ggplot2) #Loading the ggplot package
pi <- ggplot(Statisticsexs,aes(x= mean_raclo, y= mean_FLB, label = rownames(Statisticsexs))) + 
    geom_point() + 
    geom_errorbar(aes(ymin = mean_FLB-ci_FLB, ymax= mean_FLB+ci_FLB), width = 0.002, size = 0.3, color = "black") +
    geom_errorbarh(aes(xmin = mean_raclo-ci_raclo, xmax= mean_raclo+ci_raclo), width = 0.5, size = 0.3, color = "black") +
    geom_text(check_overlap = FALSE, vjust = 0, nudge_y = 0.15, nudge_x = 0.01 ) +
    labs(x = "[11C]Raclopride", y = "[11C]FLB-457")+
    geom_smooth(method = "lm", se = TRUE) +
    ggtitle("Correlation between mean BPND for [11C]FLB-457 and [11C]Raclopride")+
    theme(plot.title = element_text(hjust =0.5))

print(pi)
ggsave("correrr_xins.png") #Supplementary figure 1
```



Get statistics for test-retest using Granville's statistics package 'relfeas'
devtools::install_github(repo = "mathesong/relfeas") 

test-retest using relfeas - supplementary
```{r}
library(relfeas)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(gridExtra)
library(pwr)
library(knitr)

all_raclo <- merge(x = PET1_SRTM,y = PET2_SRTM,by = 'Subject')
oc <- data.frame(all_raclo$OC.x,all_raclo$OC.y)
oc1 <- gather(oc) %>%
  mutate(indiv = rep(paste0('s', 1:8), times=2))
stat_oc <- trt(oc1, 'value', 'indiv', 'key')$tidy

fc <- data.frame(all_raclo$FC.x,all_raclo$FC.y)
fc1 <- gather(fc) %>%
  mutate(indiv = rep(paste0('s', 1:8), times=2))
stat_fc <- trt(fc1, 'value', 'indiv', 'key')$tidy

tc <- data.frame(all_raclo$TC.x,all_raclo$TC.y)
tc1 <- gather(tc) %>%
  mutate(indiv = rep(paste0('s', 1:8), times=2))
stat_tc <- trt(tc1, 'value', 'indiv', 'key')$tidy

hip <- data.frame(all_raclo$HIP.x,all_raclo$HIP.y)
hip1 <- gather(hip) %>%
  mutate(indiv = rep(paste0('s', 1:8), times=2))
stat_hip <- trt(hip1, 'value', 'indiv', 'key')$tidy

tha <- data.frame(all_raclo$THA.x,all_raclo$THA.y)
tha1 <- gather(tha) %>%
  mutate(indiv = rep(paste0('s', 1:8), times=2))
stat_tha <- trt(tha1, 'value', 'indiv', 'key')$tidy

amg <- data.frame(all_raclo$AMG.x,all_raclo$AMG.y)
amg1 <- gather(amg) %>%
  mutate(indiv = rep(paste0('s', 1:8), times=2))
stat_amg <- trt(amg1, 'value', 'indiv', 'key')$tidy

cau <- data.frame(all_raclo$CAU.x,all_raclo$CAU.y)
cau1 <- gather(cau) %>%
  mutate(indiv = rep(paste0('s', 1:8), times=2))
stat_cau <- trt(cau1, 'value', 'indiv', 'key')$tidy

put <- data.frame(all_raclo$PUT.x,all_raclo$PUT.y)
put1 <- gather(put) %>%
  mutate(indiv = rep(paste0('s', 1:8), times=2))
stat_put <- trt(put1, 'value', 'indiv', 'key')$tidy

stats_raclo <- rbind(stat_oc,stat_fc,stat_tc,stat_hip,stat_tha,stat_amg,stat_cau,stat_put)
ROI <- c("OC","FC","TC","HIP","THA","AMG","CAU","PUT")
stats_raclo <- cbind(ROI,stats_raclo)
writexl::write_xlsx(stats_raclo, "X:/kipet/atlas_images/human/vff/Tove/Analysis in R/results/stats_raclo_rel.xlsx") #Part 1 of supp Table 1

#FLB:

all_flb <- merge(x = PET3_SRTM,y = PET4_SRTM,by = 'Subject')
oc <- data.frame(all_flb$OC.x,all_flb$OC.y)
oc1 <- gather(oc) %>%
  mutate(indiv = rep(paste0('s', 1:8), times=2))
stat_oc <- trt(oc1, 'value', 'indiv', 'key')$tidy

fc <- data.frame(all_flb$FC.x,all_flb$FC.y)
fc1 <- gather(fc) %>%
  mutate(indiv = rep(paste0('s', 1:8), times=2))
stat_fc <- trt(fc1, 'value', 'indiv', 'key')$tidy

tc <- data.frame(all_flb$TC.x,all_flb$TC.y)
tc1 <- gather(tc) %>%
  mutate(indiv = rep(paste0('s', 1:8), times=2))
stat_tc <- trt(tc1, 'value', 'indiv', 'key')$tidy

hip <- data.frame(all_flb$HIP.x,all_flb$HIP.y)
hip1 <- gather(hip) %>%
  mutate(indiv = rep(paste0('s', 1:8), times=2))
stat_hip <- trt(hip1, 'value', 'indiv', 'key')$tidy

tha <- data.frame(all_flb$THA.x,all_flb$THA.y)
tha1 <- gather(tha) %>%
  mutate(indiv = rep(paste0('s', 1:8), times=2))
stat_tha <- trt(tha1, 'value', 'indiv', 'key')$tidy

amg <- data.frame(all_flb$AMG.x,all_flb$AMG.y)
amg1 <- gather(amg) %>%
  mutate(indiv = rep(paste0('s', 1:8), times=2))
stat_amg <- trt(amg1, 'value', 'indiv', 'key')$tidy

cau <- data.frame(all_flb$CAU.x,all_flb$CAU.y)
cau1 <- gather(cau) %>%
  mutate(indiv = rep(paste0('s', 1:8), times=2))
stat_cau <- trt(cau1, 'value', 'indiv', 'key')$tidy

put <- data.frame(all_flb$PUT.x,all_flb$PUT.y)
put1 <- gather(put) %>%
  mutate(indiv = rep(paste0('s', 1:8), times=2))
stat_put <- trt(put1, 'value', 'indiv', 'key')$tidy

stats_flb <- rbind(stat_oc,stat_fc,stat_tc,stat_hip,stat_tha,stat_amg,stat_cau,stat_put)
ROI <- c("OC","FC","TC","HIP","THA","AMG","CAU","PUT")
stats_flb <- cbind(ROI,stats_flb)
writexl::write_xlsx(stats_flb, "X:/kipet/atlas_images/human/vff/Tove/Analysis in R/results/stats_flb_rel.xlsx") #part 1 of supp table 2
```

Simplified TrT for raclo
- for supp Table 1
```{r}
Rac1 <- NULL
Rac2 <- NULL

all_raclo <- NULL
all_raclo <- data.frame()
raclo_morning <- PET1_SRTM[,-c(7,9)] #remove data for insula and cer!
colnames(raclo_morning)<-c("Subject","FC_morning","OC_morning","TC_morning","AMG_morning","CAU_morning","HIP_morning","PUT_morning","THA_morning")



raclo_afternoon <-PET2_SRTM[,-c(7,9)]
colnames(raclo_afternoon)<- c("Subject","FC_afternoon","OC_afternoon","TC_afternoon","AMG_afternoon","CAU_afternoon","HIP_afternoon","PUT_afternoon","THA_afternoon")
all_raclo <- merge(x = raclo_morning,raclo_afternoon,by = 'Subject') 

Rac1 <- rbind(Rac1, summarySE(data = all_raclo, measurevar = "OC_morning"))
Rac1 <- rbind(Rac1, summarySE(data = all_raclo, measurevar = "FC_morning"))
Rac1 <- rbind(Rac1, summarySE(data = all_raclo, measurevar = "TC_morning"))
Rac1 <- rbind(Rac1, summarySE(data = all_raclo, measurevar = "HIP_morning"))
Rac1 <- rbind(Rac1, summarySE(data = all_raclo, measurevar = "THA_morning"))
Rac1 <- rbind(Rac1, summarySE(data = all_raclo, measurevar = "AMG_morning"))
Rac1 <- rbind(Rac1, summarySE(data = all_raclo, measurevar = "CAU_morning"))
Rac1 <- rbind(Rac1, summarySE(data = all_raclo, measurevar = "PUT_morning"))
Rac1 <- Rac1[,c(4,5)]

Rac2 <- rbind(Rac2, summarySE(data = all_raclo, measurevar = "OC_afternoon"))
Rac2 <- rbind(Rac2, summarySE(data = all_raclo, measurevar = "FC_afternoon"))
Rac2 <- rbind(Rac2, summarySE(data = all_raclo, measurevar = "TC_afternoon"))
Rac2 <- rbind(Rac2, summarySE(data = all_raclo, measurevar = "HIP_afternoon"))
Rac2 <- rbind(Rac2, summarySE(data = all_raclo, measurevar = "THA_afternoon"))
Rac2 <- rbind(Rac2, summarySE(data = all_raclo, measurevar = "AMG_afternoon"))
Rac2 <- rbind(Rac2, summarySE(data = all_raclo, measurevar = "CAU_afternoon"))
Rac2 <- rbind(Rac2, summarySE(data = all_raclo, measurevar = "PUT_afternoon"))
Rac2 <- Rac2[,c(4,5)]


ROI <- c("OC","FC","TC","HIP","THA","AMG","CAU","PUT")
SEM <- Statistics$se_raclo
trt_simple_rac <- cbind(ROI,Rac1,Rac2,SEM)
colnames(trt_simple_rac) <- c("ROI","PET 1 mean BPND","PET 1 sd","PET 2 mean BPND","PET 2 sd","SEM")
writexl::write_xlsx(trt_simple_rac, "X:/kipet/atlas_images/human/vff/Tove/Analysis in R/results/trt_simple_rac.xlsx") #Column 1-3 of supp table 1.
```

Simplified Trt FLB

Supp table 2
:::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
::::::::::::::::
```{r}
FLB1 <- NULL
FLB2 <- NULL

all_FLB <-NULL
all_FLB <- data.frame()
FLB_morning <- PET3_SRTM[,-c(7,9)]
colnames(FLB_morning)<-c("Subject","FC_morning","OC_morning","TC_morning","AMG_morning","CAU_morning","HIP_morning","PUT_morning","THA_morning")

FLB_afternoon <- PET4_SRTM[,-c(7,9)]
colnames(FLB_afternoon)<- c("Subject","FC_afternoon","OC_afternoon","TC_afternoon","AMG_afternoon","CAU_afternoon","HIP_afternoon","PUT_afternoon","THA_afternoon")

all_FLB <- merge(x = FLB_morning,FLB_afternoon,by = 'Subject')

FLB1 <- rbind(FLB1, summarySE(data = all_FLB, measurevar = "OC_morning"))
FLB1 <- rbind(FLB1, summarySE(data = all_FLB, measurevar = "FC_morning"))
FLB1 <- rbind(FLB1, summarySE(data = all_FLB, measurevar = "TC_morning"))
FLB1 <- rbind(FLB1, summarySE(data = all_FLB, measurevar = "HIP_morning"))
FLB1 <- rbind(FLB1, summarySE(data = all_FLB, measurevar = "THA_morning"))
FLB1 <- rbind(FLB1, summarySE(data = all_FLB, measurevar = "AMG_morning"))
FLB1 <- rbind(FLB1, summarySE(data = all_FLB, measurevar = "CAU_morning"))
FLB1 <- rbind(FLB1, summarySE(data = all_FLB, measurevar = "PUT_morning"))
FLB1 <- FLB1[,c(4,5)]

FLB2 <- rbind(FLB2, summarySE(data = all_FLB, measurevar = "OC_afternoon"))
FLB2 <- rbind(FLB2, summarySE(data = all_FLB, measurevar = "FC_afternoon"))
FLB2 <- rbind(FLB2, summarySE(data = all_FLB, measurevar = "TC_afternoon"))
FLB2 <- rbind(FLB2, summarySE(data = all_FLB, measurevar = "HIP_afternoon"))
FLB2 <- rbind(FLB2, summarySE(data = all_FLB, measurevar = "THA_afternoon"))
FLB2 <- rbind(FLB2, summarySE(data = all_FLB, measurevar = "AMG_afternoon"))
FLB2 <- rbind(FLB2, summarySE(data = all_FLB, measurevar = "CAU_afternoon"))
FLB2 <- rbind(FLB2, summarySE(data = all_FLB, measurevar = "PUT_afternoon"))
FLB2 <- FLB2[,c(4,5)]

ROI <- c("OC","FC","TC","HIP","THA","AMG","CAU","PUT")
SEMf <- Statistics$se_FLB
trt_simple_flb <- cbind(ROI,FLB1,FLB2,SEMf)
colnames(trt_simple_flb) <- c("ROI","PET 1 mean BPND","PET 1 sd","PET 2 mean BPND","PET 2 sd","SEM")

writexl::write_xlsx(trt_simple_flb, "X:/kipet/atlas_images/human/vff/Tove/Analysis in R/results/trt_simple_flb.xlsx") #Column 1-3 of supp table 2.
```


